I don't know, are you sure you want to do this?

### 2016-10-11 submission/paper.tex
solving conflict

%\documentclass[wrr]{agutex}
\documentclass[wrr, draft]{agutex}
% Author names in capital letters:
\authorrunninghead{1st AUTHOR ET AL.}

% Shorter version of title entered in capital letters:
\titlerunninghead{ADAPTING TO UNCERTAIN SEA LEVEL RISE}

%Corresponding author mailing address and e-mail address:
\authoraddr{Corresponding author: Name, Address. (email)}

\usepackage{bbm, amsmath}
%\usepackage[dvips]{graphicx}
\usepackage{graphicx}
\setkeys{Gin}{draft=false}
\usepackage{paralist, booktabs}
\usepackage{url}
\usepackage{color}

\usepackage{lineno}
 \linenumbers*[1]
%  To add line numbers to lines with equations:

\begin{document}

%% ------------------------------------------------------------------------ %%
%  TITLE
%% ------------------------------------------------------------------------ %%

\title{I don't know, are you sure you want to do this?}

%% ------------------------------------------------------------------------ %%
%  AUTHORS AND AFFILIATIONS
%% ------------------------------------------------------------------------ %%

% \altaffilmark will produce footnote;
% matching \altaffiltext will appear at bottom of page.

\authors{T. Thorarinsdottir\altaffilmark{1}, P. Guttorp\altaffilmark{1}, M. Drews\altaffilmark{2}}

\altaffiltext{1}{Norwegian Computing Centere}

\altaffiltext{2}{Danish Technological University}

\altaffiltext{3}{Affiliation three}

%% ------------------------------------------------------------------------ %%
%  ABSTRACT
%% ------------------------------------------------------------------------ %%

\begin{abstract}
...
\end{abstract}

%% ------------------------------------------------------------------------ %%
%  BEGIN ARTICLE
%% ------------------------------------------------------------------------ %%

\begin{article}

\section{Introduction}\label{sec:intro}

\section{Sea level projections {\color{blue} (PG)}}

\subsection{Global sea level}
Most climate models do not explicitly provide sea level as an output of the calculations. Rather, the IPCC AR5 report \citep[ch.~13]{ipcc} combines the heat expansion of the ocean with temperature forced models for glacial melt, Greenland ice melt, and Antarctic ice melt and with land rise due to rebound from the last ice age. Judging from the supplementary material to \citet[ch.~13]{ipcc}, the uncertainty assessment is only based on the spread of the ensemble of temperature projections, not on the additional uncertainty in the ice models used.

We will instead use the empirical approach of Rahmstorf and collaborators \citep{Rahmstorf07,Rahmstorf11}, employing the statistical modeling of \citet{Bolin2014a} to relate global annual mean temperature anomalies \citep{giss} to global mean sea level anomalies \citep{csiro}.

%Figure showing historical relationship?

We then apply the estimated historical relationship to projected temperatures from the CMIP5 experiment \citep{cmip5} to obtain projected global annual mean sea level, taking into account the uncertainty in the statistical model as well as the spread of the temperature projection ensemble (see subsection \ref{unc_ass}). 
%Figure with sea level projections & IPCC projections?

\subsection{Local sea level}
In order to get from global sea level projections to local ones, it is important to note that sea level rise not is uniform over the globe. Glacial and land ice melting affect the local sea level differently depending on where the melted ice is located.
%Gravitaional effects
Another major effect in Fennoskandia is the land rise due to isostatic rebound from the glaciers of the last ice age. 
Again, we will use historical data to relate global sea level to isostatically corrected local sea level using a time series regression model. 
%Figure showing corrected and uncorrected Bergen data and regression model.

The local sea level projections are then obtained by first relating projected temperature to global sea level, and then relating the global sea level to the local one. Each climate model temperature projection yields a different local sea level projection.

\subsection{Uncertainty assessment}
\label{unc_ass}
Following the approach of \citet{Guttorp2014} we assess the uncertainty in the local sea level projections taking into account the variability between the climate projections used, the uncertainties in the regressions of global mean temperature on global mean sea level and of global on local sea level. We express the sea level projection uncertainty in terms of a confidence band that is simultaneously of the intended  level  for all projection years. This allows us, for example, to get a confidence band for the years when a given sea level rise is obtained.

%Figure showing Bergen and Copenhagen slr projections

\subsection{Limitations of the sea level projections}
The main assumption is using historical relationships in statistical projections of the type used in this paper is that there is no major change in how temperature relates to sea level, globally and locally. Among the factors that may invalidate this approach are changes in water storage on land (removing water from the oceans), excessive siphoning of groundwater (resulting in land subsidence), changes in the rates of glacial and land ice melt, and changes in Earth's gravitational field due to transfer of mass from land ice to ocean water. For example, the rate of ice melt on Greenland may suddenly increase substantially due to intense warming of both air and sea water. Our current climate models are not able to resolve the ice processes sufficiently to include such so called tipping points into the projections. Also, the IPCC scenarios do not include changes in water usage \citep{change}.

\section{Decision tools {\color{blue} (KdB, MD, TT)}}

\subsection{Timing of adaptation measures}

We consider adaptation decision making related to the timing of proactive adaptation measures. That is, the goal is to adapt to sea level rise before major damages occur. In a cost-benefit framework, an investment should be delayed as long as the benefits of delay (avoided investment costs) are greater than the associated costs (higher climate change damages) \citep{Fankhauser&1999}.

\cite{Fankhauser&1999} describe a deterministic framework where an adaptation investment of $C^0$ now (at time $n=0$) leads to unmitigated damage of $d_0^0$ in period $0$, and a stream of partially mitigated damages $d_t^0$ in periods $t=1,2,\ldots$. If $r$ is the discount rate, the net present value damage, $D^0$, associated with this investment is
\begin{linenomath*}
\begin{equation}\label{eq:deterministic damage}
D^0 = C^0 + d_0^0 + \frac{d_1^0}{1+r} + \frac{d_2^0}{(1+r)^2} + \cdots  
\end{equation}
\end{linenomath*}
In comparison, postponing the adaptation investment to time period $n=1$ would lead to unmitigated damages in periods $0$ and $1$, and partially mitigated damages, $d_t^1$, thereafter. The delay would be preferable if
\begin{linenomath*}
\[
C^0 - \frac{C^1}{(1+r)} > (d_0^1 - d_0^0) + \frac{d_1^1 - d_1^0}{1+r} + \frac{d_2^1 - d_2^0}{(1+r)^2} + \cdots
\]
\end{linenomath*}
Here, the expression on the left describes the benefits of the delay while the expression on the right describes the cost of the delay. In the simplest case, there is no change in investment costs ($C^0 = C^1 = C$) and the delay has no lasting effects beyond period 1 ($d_t^1 = d_t^0$ for $t > 1$). In this case, the comparison is between the expected return $r$ earned on the captial while implementation is delayed and one addtional time period of unmitigated damage,
\begin{linenomath*}
  \[
  r C > d_1^1 - d_1^0.
  \]
  \end{linenomath*}

\subsection{Limitations of the decision framework}

\section{Case studies}

\subsection{Data {\color{blue} (PG)}}

\subsection{Timing of adaptation measures {\color{blue} (KdB, TT)}}

A case study focusing on and comparing different cities in Norway.

\subsection{Selection of adaptation measures(?) {\color{blue} (MD)}}

A case study focusing on Denmark.

\section{Conclusions}

%  ACKNOWLEDGMENTS
\begin{acknowledgments}
This work was funded by NordForsk through project number 74456 ``Statistical Analysis of Climate Projections'' (eSACP) and The Research Council of Norway through project number 243953 ``Physical and Statistical Analysis of Climate Extremes in Large Datasets'' (ClimateXL). The source code for the analysis is implemented in the statistical programming language {\tt R} (\url{http://www.R-project.org}) and is available on GitHub at \url{http://github.com/eSACP/...}.
\end{acknowledgments}

%%  REFERENCE LIST AND TEXT CITATIONS
% 5\bibliographystyle{../BibTeX/agufull08}
\bibliographystyle{agufull08}
\bibliography{ref.bib}
% Please use ONLY \citet and \citep for reference citations.

%\begin{thebibliography}{37}
%%   Before submitting: copy all the contents into the .bbl LaTeX file here
%%   and run latex again
%\providecommand{\natexlab}[1]{#1}
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi

%\end{thebibliography}

%% ------------------------------------------------------------------------ %%
%  END ARTICLE
%% ------------------------------------------------------------------------ %%
\end{article}

%% Enter Figures and Tables here:

\end{document}

>>>>

<!DOCTYPE html>
<html lang="en" class=" is-copy-enabled is-u2f-enabled">
  <head prefix="og: http://ogp.me/ns# fb: http://ogp.me/ns/fb# object: http://ogp.me/ns/object# article: http://ogp.me/ns/article# profile: http://ogp.me/ns/profile#">
    <meta charset='utf-8'>
    <meta content="origin-when-cross-origin" name="referrer" />

    <link crossorigin="anonymous" href="https://assets-cdn.github.com/assets/frameworks-cb4ede7df6d8670c4051172e4d6bc6916b3c765fa15b4ee9b348f157fdb85114.css" integrity="sha256-y07effbYZwxAURcuTWvGkWs8dl+hW07ps0jxV/24URQ=" media="all" rel="stylesheet" />
    <link crossorigin="anonymous" href="https://assets-cdn.github.com/assets/github-f32b0e7dbc73ab49677d48d959274568a459569efc1cf486e83fe9aed5890998.css" integrity="sha256-8ysOfbxzq0lnfUjZWSdFaKRZVp78HPSG6D/prtWJCZg=" media="all" rel="stylesheet" />

    <meta http-equiv="X-UA-Compatible" content="IE=edge">
    <meta http-equiv="Content-Language" content="en">
    <meta name="viewport" content="width=device-width">

    <title>SeaLevelDecisions/paper.tex at master · eSACP/SeaLevelDecisions</title>
    <link rel="search" type="application/opensearchdescription+xml" href="/opensearch.xml" title="GitHub">
    <link rel="fluid-icon" href="https://github.com/fluidicon.png" title="GitHub">
    <link rel="apple-touch-icon" href="/apple-touch-icon.png">
    <link rel="apple-touch-icon" sizes="57x57" href="/apple-touch-icon-57x57.png">
    <link rel="apple-touch-icon" sizes="60x60" href="/apple-touch-icon-60x60.png">
    <link rel="apple-touch-icon" sizes="72x72" href="/apple-touch-icon-72x72.png">
    <link rel="apple-touch-icon" sizes="76x76" href="/apple-touch-icon-76x76.png">
    <link rel="apple-touch-icon" sizes="114x114" href="/apple-touch-icon-114x114.png">
    <link rel="apple-touch-icon" sizes="120x120" href="/apple-touch-icon-120x120.png">
    <link rel="apple-touch-icon" sizes="144x144" href="/apple-touch-icon-144x144.png">
    <link rel="apple-touch-icon" sizes="152x152" href="/apple-touch-icon-152x152.png">
    <link rel="apple-touch-icon" sizes="180x180" href="/apple-touch-icon-180x180.png">
    <meta property="fb:app_id" content="1401488693436528">

      <meta content="https://avatars1.githubusercontent.com/u/14945390?v=3&amp;s=400" name="twitter:image:src" /><meta content="@github" name="twitter:site" /><meta content="summary" name="twitter:card" /><meta content="eSACP/SeaLevelDecisions" name="twitter:title" /><meta content="SeaLevelDecisions - Paper on sea level change adaptation decision making under uncertainty " name="twitter:description" />
      <meta content="https://avatars1.githubusercontent.com/u/14945390?v=3&amp;s=400" property="og:image" /><meta content="GitHub" property="og:site_name" /><meta content="object" property="og:type" /><meta content="eSACP/SeaLevelDecisions" property="og:title" /><meta content="https://github.com/eSACP/SeaLevelDecisions" property="og:url" /><meta content="SeaLevelDecisions - Paper on sea level change adaptation decision making under uncertainty " property="og:description" />
      <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">
    <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">
    <link rel="assets" href="https://assets-cdn.github.com/">
    <link rel="web-socket" href="wss://live.github.com/_sockets/MTQ5NDUyMTM6MDUyNDYzZDIwMmVhNjNkYzMwNWI5ZWU1M2Q3NmQ3MWQ6NmY5MTBmMGJhNDA4NDZkNzQ4MGRkNDBjODdkYjBmYTI4ZjBkODAzMWJiY2IzODI3YWE5MDI3MGRjZTc0MjBkMQ==--89d25bdd8d4ae8902ca35bc19bf81c83badb6ba1">
    <meta name="pjax-timeout" content="1000">
    <link rel="sudo-modal" href="/sessions/sudo_modal">
    <meta name="request-id" content="9C740835:0C52:28EFDD9:57FCCA5A" data-pjax-transient>

    <meta name="msapplication-TileImage" content="/windows-tile.png">
    <meta name="msapplication-TileColor" content="#ffffff">
    <meta name="selected-link" value="repo_source" data-pjax-transient>

    <meta name="google-site-verification" content="KT5gs8h0wvaagLKAVWq8bbeNwnZZK1r1XQysX3xurLU">
<meta name="google-site-verification" content="ZzhVyEFwb7w3e0-uOTltm8Jsck2F5StVihD0exw2fsA">
    <meta name="google-analytics" content="UA-3769691-2">

<meta content="collector.githubapp.com" name="octolytics-host" /><meta content="github" name="octolytics-app-id" /><meta content="9C740835:0C52:28EFDD9:57FCCA5A" name="octolytics-dimension-request_id" /><meta content="14945213" name="octolytics-actor-id" /><meta content="thordislinda" name="octolytics-actor-login" /><meta content="25d4553f8e8b0f7d5f53a85da67d6ac37df8675bf0532ac0ed5d5f1cf648984f" name="octolytics-actor-hash" />
<meta content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-pjax-transient="true" name="analytics-location" />

  <meta class="js-ga-set" name="dimension1" content="Logged In">

        <meta name="hostname" content="github.com">
    <meta name="user-login" content="thordislinda">

        <meta name="expected-hostname" content="github.com">
      <meta name="js-proxy-site-detection-payload" content="Y2ExZjFiMDljMmQxNzBiYjUzNWQzYjgxYmI2OGM1NzY0Nzc1NGRmNWJhNGVmNDNjOTJkYjc0NmJlOTA5ZGU1MXx7InJlbW90ZV9hZGRyZXNzIjoiMTU2LjExNi44LjUzIiwicmVxdWVzdF9pZCI6IjlDNzQwODM1OjBDNTI6MjhFRkREOTo1N0ZDQ0E1QSIsInRpbWVzdGFtcCI6MTQ3NjE4NDY3MX0=">

      <link rel="mask-icon" href="https://assets-cdn.github.com/pinned-octocat.svg" color="#4078c0">
      <link rel="icon" type="image/x-icon" href="https://assets-cdn.github.com/favicon.ico">

    <meta name="html-safe-nonce" content="45264389604d630702d1147e97655f012ab39c1a">
    <meta content="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" name="form-nonce" />

    <meta http-equiv="x-pjax-version" content="5773d60f3601ed21fb6ed8e0c6eff2f6">

  <meta name="description" content="SeaLevelDecisions - Paper on sea level change adaptation decision making under uncertainty ">
  <meta name="go-import" content="github.com/eSACP/SeaLevelDecisions git https://github.com/eSACP/SeaLevelDecisions.git">

  <meta content="14945390" name="octolytics-dimension-user_id" /><meta content="eSACP" name="octolytics-dimension-user_login" /><meta content="69018538" name="octolytics-dimension-repository_id" /><meta content="eSACP/SeaLevelDecisions" name="octolytics-dimension-repository_nwo" /><meta content="false" name="octolytics-dimension-repository_public" /><meta content="false" name="octolytics-dimension-repository_is_fork" /><meta content="69018538" name="octolytics-dimension-repository_network_root_id" /><meta content="eSACP/SeaLevelDecisions" name="octolytics-dimension-repository_network_root_nwo" />
  <link href="https://github.com/eSACP/SeaLevelDecisions/commits/master.atom?token=AOQLvX3BJqaD2T7TXulS-nsUHBg8-hiIks62CLlvwA%3D%3D" rel="alternate" title="Recent Commits to SeaLevelDecisions:master" type="application/atom+xml">

      <link rel="canonical" href="https://github.com/eSACP/SeaLevelDecisions/blob/master/submission/paper.tex" data-pjax-transient>
  </head>

  <body class="logged-in  env-production linux vis-private page-blob">
    <div id="js-pjax-loader-bar" class="pjax-loader-bar"><div class="progress"></div></div>
    <a href="#start-of-content" tabindex="1" class="accessibility-aid js-skip-to-content">Skip to content</a>

        <div class="header header-logged-in true" role="banner">
  <div class="container clearfix">

    <a class="header-logo-invertocat" href="https://github.com/" data-hotkey="g d" aria-label="Homepage" data-ga-click="Header, go to dashboard, icon:logo">
  <svg aria-hidden="true" class="octicon octicon-mark-github" height="28" version="1.1" viewBox="0 0 16 16" width="28"><path d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"></path></svg>
</a>

        <div class="header-search scoped-search site-scoped-search js-site-search" role="search">
  <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/search" class="js-site-search-form" data-scoped-search-url="/eSACP/SeaLevelDecisions/search" data-unscoped-search-url="/search" method="get"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /></div>
    <label class="form-control header-search-wrapper js-chromeless-input-container">
      <div class="header-search-scope">This repository</div>
      <input type="text"
        class="form-control header-search-input js-site-search-focus js-site-search-field is-clearable"
        data-hotkey="s"
        name="q"
        placeholder="Search"
        aria-label="Search this repository"
        data-unscoped-placeholder="Search GitHub"
        data-scoped-placeholder="Search"
        autocapitalize="off">
    </label>
</form></div>

      <ul class="header-nav float-left" role="navigation">
        <li class="header-nav-item">
          <a href="/pulls" aria-label="Pull requests you created" class="js-selected-navigation-item header-nav-link" data-ga-click="Header, click, Nav menu - item:pulls context:user" data-hotkey="g p" data-selected-links="/pulls /pulls/assigned /pulls/mentioned /pulls">
            Pull requests
</a>        </li>
        <li class="header-nav-item">
          <a href="/issues" aria-label="Issues you created" class="js-selected-navigation-item header-nav-link" data-ga-click="Header, click, Nav menu - item:issues context:user" data-hotkey="g i" data-selected-links="/issues /issues/assigned /issues/mentioned /issues">
            Issues
</a>        </li>
          <li class="header-nav-item">
            <a class="header-nav-link" href="https://gist.github.com/" data-ga-click="Header, go to gist, text:gist">Gist</a>
          </li>
      </ul>

<ul class="header-nav user-nav float-right" id="user-links">
  <li class="header-nav-item">

    <a href="/notifications" aria-label="You have no unread notifications" class="header-nav-link notification-indicator tooltipped tooltipped-s js-socket-channel js-notification-indicator" data-channel="tenant:1:notification-changed:14945213" data-ga-click="Header, go to notifications, icon:read" data-hotkey="g n">
        <span class="mail-status "></span>
        <svg aria-hidden="true" class="octicon octicon-bell" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M14 12v1H0v-1l.73-.58c.77-.77.81-2.55 1.19-4.42C2.69 3.23 6 2 6 2c0-.55.45-1 1-1s1 .45 1 1c0 0 3.39 1.23 4.16 5 .38 1.88.42 3.66 1.19 4.42l.66.58H14zm-7 4c1.11 0 2-.89 2-2H5c0 1.11.89 2 2 2z"></path></svg>
</a>
  </li>

  <li class="header-nav-item dropdown js-menu-container">
    <a class="header-nav-link tooltipped tooltipped-s js-menu-target" href="/new"
       aria-label="Create new…"
       data-ga-click="Header, create new, icon:add">
      <svg aria-hidden="true" class="octicon octicon-plus float-left" height="16" version="1.1" viewBox="0 0 12 16" width="12"><path d="M12 9H7v5H5V9H0V7h5V2h2v5h5z"></path></svg>
      <span class="dropdown-caret"></span>
    </a>

    <div class="dropdown-menu-content js-menu-content">
      <ul class="dropdown-menu dropdown-menu-sw">

<a class="dropdown-item" href="/new" data-ga-click="Header, create new repository">
  New repository
</a>

  <a class="dropdown-item" href="/new/import" data-ga-click="Header, import a repository">
    Import repository
  </a>

  <a class="dropdown-item" href="/organizations/new" data-ga-click="Header, create new organization">
    New organization
  </a>

  <div class="dropdown-divider"></div>
  <div class="dropdown-header">
    <span title="eSACP">This organization</span>
  </div>
  <a class="dropdown-item" href="/orgs/eSACP/people#invite-member" data-ga-click="Header, invite someone">
    Invite someone
  </a>
  <a class="dropdown-item" href="/orgs/eSACP/new-team" data-ga-click="Header, create new team">
    New team
  </a>
  <a class="dropdown-item" href="/organizations/eSACP/repositories/new" data-ga-click="Header, create new organization repository, icon:repo">
    New repository
  </a>

  <div class="dropdown-divider"></div>
  <div class="dropdown-header">
    <span title="eSACP/SeaLevelDecisions">This repository</span>
  </div>
    <a class="dropdown-item" href="/eSACP/SeaLevelDecisions/issues/new" data-ga-click="Header, create new issue">
      New issue
    </a>
    <a class="dropdown-item" href="/eSACP/SeaLevelDecisions/settings/collaboration" data-ga-click="Header, create new collaborator">
      New collaborator
    </a>

      </ul>
    </div>
  </li>

  <li class="header-nav-item dropdown js-menu-container">
    <a class="header-nav-link name tooltipped tooltipped-sw js-menu-target" href="/thordislinda"
       aria-label="View profile and more"
       data-ga-click="Header, show menu, icon:avatar">
      <img alt="@thordislinda" class="avatar" height="20" src="https://avatars1.githubusercontent.com/u/14945213?v=3&amp;s=40" width="20" />
      <span class="dropdown-caret"></span>
    </a>

    <div class="dropdown-menu-content js-menu-content">
      <div class="dropdown-menu dropdown-menu-sw">
        <div class="dropdown-header header-nav-current-user css-truncate">
          Signed in as <strong class="css-truncate-target">thordislinda</strong>
        </div>

        <div class="dropdown-divider"></div>

        <a class="dropdown-item" href="/thordislinda" data-ga-click="Header, go to profile, text:your profile">
          Your profile
        </a>
        <a class="dropdown-item" href="/thordislinda?tab=stars" data-ga-click="Header, go to starred repos, text:your stars">
          Your stars
        </a>
        <a class="dropdown-item" href="/explore" data-ga-click="Header, go to explore, text:explore">
          Explore
        </a>
          <a class="dropdown-item" href="/integrations" data-ga-click="Header, go to integrations, text:integrations">
            Integrations
          </a>
        <a class="dropdown-item" href="https://help.github.com" data-ga-click="Header, go to help, text:help">
          Help
        </a>

        <div class="dropdown-divider"></div>

        <a class="dropdown-item" href="/settings/profile" data-ga-click="Header, go to settings, icon:settings">
          Settings
        </a>

        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/logout" class="logout-form" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="3yXD4WZhwnWJytG55fL3EwgkMSCMjYlEpuhXXi1XrsllPkR2n1RGivgoBFTGcsqjYxx3Jj0qwtsKsr9Lfl+eRQ==" /></div>
          <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout">
            Sign out
          </button>
</form>      </div>
    </div>
  </li>
</ul>

  </div>
</div>

    <div id="start-of-content" class="accessibility-aid"></div>

      <div id="js-flash-container">
</div>

    <div role="main">
        <div itemscope itemtype="http://schema.org/SoftwareSourceCode">
    <div id="js-repo-pjax-container" data-pjax-container>

<div class="pagehead repohead instapaper_ignore readability-menu experiment-repo-nav">
  <div class="container repohead-details-container">

<ul class="pagehead-actions">

  <li>
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/notifications/subscribe" class="js-social-container" data-autosubmit="true" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="ow3eH8530MPPaY+NBuQQ2cKNOZgKM52lzUCopLpBByIcEQvPDDXmUb+PxjlwNE8m1o6yftRt4YK14tIqIWRMUQ==" /></div>      <input class="form-control" id="repository_id" name="repository_id" type="hidden" value="69018538" />

        <div class="select-menu js-menu-container js-select-menu">
          <a href="/eSACP/SeaLevelDecisions/subscription"
            class="btn btn-sm btn-with-count select-menu-button js-menu-target" role="button" tabindex="0" aria-haspopup="true"
            data-ga-click="Repository, click Watch settings, action:blob#show">
            <span class="js-select-button">
              <svg aria-hidden="true" class="octicon octicon-eye" height="16" version="1.1" viewBox="0 0 16 16" width="16"><path d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"></path></svg>
              Unwatch
            </span>
          </a>
          <a class="social-count js-social-count"
            href="/eSACP/SeaLevelDecisions/watchers"
            aria-label="10 users are watching this repository">
            10
          </a>

        <div class="select-menu-modal-holder">
          <div class="select-menu-modal subscription-menu-modal js-menu-content" aria-hidden="true">
            <div class="select-menu-header js-navigation-enable" tabindex="-1">
              <svg aria-label="Close" class="octicon octicon-x js-menu-close" height="16" role="img" version="1.1" viewBox="0 0 12 16" width="12"><path d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48z"></path></svg>
              <span class="select-menu-title">Notifications</span>
            </div>

              <div class="select-menu-list js-navigation-container" role="menu">

                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
                  <svg aria-hidden="true" class="octicon octicon-check select-menu-item-icon" height="16" version="1.1" viewBox="0 0 12 16" width="12"><path d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5z"></path></svg>
                  <div class="select-menu-item-text">
                    <input id="do_included" name="do" type="radio" value="included" />
                    <span class="select-menu-item-heading">Not watching</span>
                    <span class="description">Be notified when participating or @mentioned.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg aria-hidden="true" class="octicon octicon-eye" height="16" version="1.1" viewBox="0 0 16 16" width="16"><path d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"></path></svg>
                      Watch
                    </span>
                  </div>
                </div>

                <div class="select-menu-item js-navigation-item selected" role="menuitem" tabindex="0">
                  <svg aria-hidden="true" class="octicon octicon-check select-menu-item-icon" height="16" version="1.1" viewBox="0 0 12 16" width="12"><path d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5z"></path></svg>
                  <div class="select-menu-item-text">
                    <input checked="checked" id="do_subscribed" name="do" type="radio" value="subscribed" />
                    <span class="select-menu-item-heading">Watching</span>
                    <span class="description">Be notified of all conversations.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg aria-hidden="true" class="octicon octicon-eye" height="16" version="1.1" viewBox="0 0 16 16" width="16"><path d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"></path></svg>
                      Unwatch
                    </span>
                  </div>
                </div>

                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
                  <svg aria-hidden="true" class="octicon octicon-check select-menu-item-icon" height="16" version="1.1" viewBox="0 0 12 16" width="12"><path d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5z"></path></svg>
                  <div class="select-menu-item-text">
                    <input id="do_ignore" name="do" type="radio" value="ignore" />
                    <span class="select-menu-item-heading">Ignoring</span>
                    <span class="description">Never be notified.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg aria-hidden="true" class="octicon octicon-mute" height="16" version="1.1" viewBox="0 0 16 16" width="16"><path d="M8 2.81v10.38c0 .67-.81 1-1.28.53L3 10H1c-.55 0-1-.45-1-1V7c0-.55.45-1 1-1h2l3.72-3.72C7.19 1.81 8 2.14 8 2.81zm7.53 3.22l-1.06-1.06-1.97 1.97-1.97-1.97-1.06 1.06L11.44 8 9.47 9.97l1.06 1.06 1.97-1.97 1.97 1.97 1.06-1.06L13.56 8l1.97-1.97z"></path></svg>
                      Stop ignoring
                    </span>
                  </div>
                </div>

              </div>

            </div>
          </div>
        </div>
</form>
  </li>

  <li>

  <div class="js-toggler-container js-social-container starring-container ">

    <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/unstar" class="starred" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="8jsT4FwhRy7KoSwMyDFFxWSrBfQf9q6Lff0fzQ8MdEJMZInhum5hVH/n3iXzf6+xNASq1AZqI4hBSUEtSLrMxA==" /></div>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Unstar this repository" title="Unstar eSACP/SeaLevelDecisions"
        data-ga-click="Repository, click unstar button, action:blob#show; text:Unstar">
        <svg aria-hidden="true" class="octicon octicon-star" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74z"></path></svg>
        Unstar
      </button>
        <a class="social-count js-social-count" href="/eSACP/SeaLevelDecisions/stargazers"
           aria-label="0 users starred this repository">
          0
        </a>
</form>
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/star" class="unstarred" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="ks2hkl+V8bZA/NAEAqFMMvvxD9L863yDs4o1AGfGlBRqFH/bqDT71HtOaVIWzDHnNEB4JjA7PZjbQqVS5B4k9w==" /></div>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Star this repository" title="Star eSACP/SeaLevelDecisions"
        data-ga-click="Repository, click star button, action:blob#show; text:Star">
        <svg aria-hidden="true" class="octicon octicon-star" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74z"></path></svg>
        Star
      </button>
        <a class="social-count js-social-count" href="/eSACP/SeaLevelDecisions/stargazers"
           aria-label="0 users starred this repository">
          0
        </a>
</form>  </div>

  </li>
